Figures to insert in text

### 2018-03-06 Chapters/Chapter02.tex
sdm conclusion

@@

Let us revisit, in this concluding thoughts, the emphasis employed over speed of computation.  At first sight, that might seem like a typical objective of efficiency in computer science. But we are not only interested in the computer sciece effects here --- the ambition is different. More important than this `computer-sciency' goal, i.e., a beautiful, clean, efficient algorithm with the primary effect of enhanced speed, however, is the secondary effect on the sociology of science:  \emph{We can see farther}.

>>>>

\section{Number of activated hard-locations}

In his seminal work, Kanerva proposed to use a sample of 1,000,000 hard-locations in a 1,000 bits SDM. He also proposed to activate only 1,000 of them, on average. He calculated that an access radius of $r=451$ would activate, on average, 0.00107185004892 of the whole space, or, in this case, 1,071.85 hard-locations.

We extended his results, calculating the distribution of the number of activated hard-locations. As each hard-location has probability $p=0.00107185004892$ of being activated, the probability of activating exactly $a$ out of $H$ hard-locations follows a binomial distribution with mean $\mu = pH$ and standard deviation $\sigma = \sqrt{Hp(p-1)}$. In this case, $\mu = 1071.85$ and $\sigma = 32.72$.

In order to validate our scan algorithm, we have run 10,000 scans from a random bitstring and counted the number of activated hard-locations. The code is available in the ``Number of activated hard-locations'' notebook \citep{sdmframework}.

In figure \ref{fig:validation-activated-hls}, we can notice that the theoretical model and the simulation matches. Hence, it seems that both the address space generation algotihm and the scan algorithm work properly. Notice that the curve is almost the same for $n=1,000$ and $n=256$. It happens because the access radius is adjust to have $p$ as close as possible to $0.001$. They are not exactly the same because their $p$ differs a little.

\begin{figure}[!htb]
  \centering
  \subfloat[$n=1,000$, $H=1,000,000$,\protect\\ $r=451$, and $p=0.00107185$ ]{\includegraphics[width=0.5\textwidth]{./images02/new-images/activated-hls-1000.png}}
  \subfloat[$n=256$, $H=1,000,000$,\protect\\ $r=103$, and $p=0.00106684$ ]{\includegraphics[width=0.5\textwidth]{./images02/new-images/activated-hls-256.png}}

  \caption{Histogram of the number of activated hard-locations in 10,000 scans from a random bitstring. The curve in red is the theoretical normal distribution with $\mu = Hp$ and $\sigma = p(p-1)H$.}
  \label{fig:validation-activated-hls}
\end{figure}

Besides the number of activated hard-locations, we have also extended Kanerva's results to calculate the distribution of distances between the center of the circle and the activated hard-locations. Let $A$ be the set of activated hard-locations, $\xi$ be the center of the circle, and $r$ be the access radius, then:

\begin{align}
P(\text{d}(a, \xi)=x | a \in A) &= \frac{P(\text{d}(a, \xi)=x)}{P(d \in A)} \\
    &= \frac{\binom{n}{x}}{\sum_{k=0}^r \binom{n}{k}} \label{eq:prob-d-inside-circle}
\end{align}

In order to check Equation \ref{eq:prob-d-inside-circle}, we have calculated the distances of the activated hard-locations to the center of 1,000 random circles. The code is available in the ``Distances of activated hard-locations'' notebook \citep{sdmframework}.

In figure \ref{fig:validation-distance-activated-hls}, we can notice that the theoretical model and the simulation matches.

\begin{figure}[!htb]
\centering\includegraphics[width=\textwidth]{./images02/new-images/distance-activated-hls.png}

\caption{Histogram of the distances of activated hard-locations to the center of the circles. The curve in red is the theoretical distribution of Equation \ref{eq:prob-d-inside-circle}
\label{fig:validation-distance-activated-hls}}
\end{figure}

\section{Intersection of two circles}

Kanerva has calculated the intersection of two circles according to the distance between their centers. The intersection is important to understand how SDM works, because it affects directly the critical distance. When $\eta_d$ is inside the critical distance, then it will converge to $\eta$. In fact, it converges because they share a sufficient amount of hard-locations, i.e., the intersection of the circle around $\eta_d$ and $\eta$ is enough to converge. For further information about the relation between the critical distance and the intersection, see \citet{brogliato2014sparse}.

We have calculated the intersection between a random bitstring (bs1) and another bitstrings (bs2) exactly $d$ bits away. The former (bs1) is just a random bitstring. The latter (bs2) was generated randomly flipping $d$ bits of bs1. The code is available in the ``Kanerva's Figure 1.2'' notebook \citep{sdmframework}.

In Figure \ref{fig:validation-intersection}, we can notice that we have obtained the same results as Kanerva. It seems that the random flipping bits algorithm and the scan algorithm work properly.

\begin{figure}[!htb]
  \centering
  \subfloat[{\citet[Figure 1.2, p.25]{Kanerva1988}} ]{\includegraphics[width=0.45\textwidth]{./images02/new-images/kanerva-table-12.jpg}}
  \subfloat[Generated by SDM-Frameworkm with $n=1,000$ ]{\includegraphics[width=0.55\textwidth]{./images02/new-images/intersection-of-circles.png}}

  \caption{Number of hard-locations in the intersection of circles around two bitstrings $x$ bits away.}
  \label{fig:validation-intersection}
\end{figure}

---

@@

Let us revisit, in these concluding thoughts, the emphasis employed over speed of computation.  At first sight, that might seem like a typical objective of efficiency in computer science. But we are not only interested in the computer science effects here --- the ambition is different. More important than this `computer-sciency' goal, i.e., a beautiful, clean, efficient algorithm with the primary effect of enhanced speed, however, is the secondary effect on the sociology of science:  \emph{We can see farther}.

If
